Vulnerability Analysis of Container Images in Neuroimaging

### 2020-02-14 paper.tex
changes after result section

In this section, we present our study methodology. We first
introduce two container tools used for our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. Later, we discuss about 
various Linux distributions and their releases. Lastly, this section
provides the description of the scanning tools used.

@@

Tools that are capable of packing and running an application in an isolated environment
are known as container tools. Alongwith an application they also pack the application's dependencies,
required libraries and configuration files for the
application to function properly. This functioning of an application in an isolated environment
is called a container. They directly run on the Host machine's kernel so they are lightweight.
Consequently, more containers can be run on a given Host machine as compared to virtual machines.

@@

%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root, and is remotely controlled through a
UNIX socket. As Docker Daemon is responsible for launching and managing containers,
when a container runs, the container is spawned as a
child process of this root owned daemon.

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
If a user gets \textit{root} privileges, it introduces unthinkable security risks
for multi-tenant shared enviornments. Due to this reason, Docker is not
supported by HPC environments.

@@

Singularity is another tool for packing and running applications in containers.

Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

@@

So we have total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table2} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

\subsubsection{Scanning tools used}
\begin{comments}
Out of the various container image scanning tools available to scan Docker images,
we selected Anchore~\cite{github_2019}
and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
Clair Scanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools. So total there are three scanners for Docker images
and one scanner for Singularity images.
\end{comments}

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
\begin{comments}
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
\end{comments}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
\begin{comments}
Anchore offers services in two ways: Anchore Engine and Anchore
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. 
\end{comments}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get vulnerability feed of various OS distribution, Anchore refers to
different sources. For example Ubuntu launchpad database is used for Ubuntu.

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{Comments}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comments}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registery to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.

@@

In this section, we present results of three experiments that are carried out to see
how the number of vulnerabilities vary inside images. First experiment involves scanning
the images. We use three different scanners
to see if all are reporting same vulnerabilities or not. Second experiment involves updating
all these images and then rescanning. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.

@@

Figure~\ref{fig:graph1} gives more image specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
light-weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian contains highest number of critical vulnerabilities among Ubuntu, Alpine, and Centos.

\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c},
        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table}

\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c|c},
	table head ={Image Tag} & {Image Name}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{names.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table2}Image names}
\end{table}

\begin{figure}[!htb]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.png}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure}[!htb]
        {\includegraphics[scale=2,width=\columnwidth]
        {Figures/vulngraph4.png}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure}

@@

Table~\ref{table1} compares results of scanning images with three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table.

We add all regions of Venn diagram
we get total 20050 vulnerabilities in Bids and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 only reported by Clair and 325 only detected by Vuls.

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

@@

Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
both Clair and Vuls.

\textbf{Linux-Kernel-Headers-} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers.
4443 out of 4453 vulnerabilities difference is due to linux-kernel-headers.
For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50 is not detected by both Vuls and Clair Scanner

\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
that release is also mentioned. For example, one reason can be that code which is creating issue is not 
present in that release etc. In other words, we can say that these are false positives by Vuls.
For example CVE-2015-2305 is not affecting package cups in Trusty.

\textbf{With status as "Ignored(reached end-of-life)"-} Some vulnerabilities have status as “ignored (reached end-of-life)”.
These vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release these vulnerabilities can be present or not.
Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve
prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
If this kind of vulnerability is present in ESM release then Clair will report it because Clair Scanner
only refers ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE", which means does not exist, then Clair Scanner will not report it. 
For example CVE-2017-9994 vulnerability. As Ubuntu LTS release is present inside the images so
Clair Scanner's reference to ESM release is wrong here.

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.

@@

\textbf{with status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find package manager inside the image and then update the image according the package manager it finds.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2}shows number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure}[!htb]
        {\includegraphics[width=\columnwidth]
        {Figures/aferupdatewithpackage.png}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure}
\subsection{Effect Of Size Reduction}

>>>>

\begin{comment}
This work involves three experiments.
First experiment involves scanning
the images. We use three different scanners
to see if all are reporting same vulnerabilities or not. Second experiment involves updating
all these images and then rescanning. The last experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image.
\end{comment}

In this section, we present our study methodology. We first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. Later, we discuss 
various Linux distributions and their releases. Lastly, this section
provides a description of the scanning tools used.

@@

Tools that are capable of packing and running an application in an isolated environment
are known as container tools. Alongwith an application they also pack the application's dependencies,
required libraries and configuration files for the
application to function properly. The functioning of an application in an isolated environment
is called a container. Containers directly run on the Host machine's kernel so they are lightweight.
Consequently, more containers can be run on a given Host machine as compared to virtual machines.

@@

%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
???BLOCK MISSING

@@

Singularity is another tool for packing and running applications in containers. 
In our experiments, we used $2.5.2$ Singularity version. 
\begin{comment}
Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.
\end{comment}

@@

So we have total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

\subsubsection{Scanning tools used}

\begin{comment}
Out of the various container image scanning tools available to scan Docker images,
we selected Anchore~\cite{github_2019}
and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
Clair Scanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools. So total there are three scanners for Docker images
and one scanner for Singularity images.
\end{comment}

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
\begin{comment}
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
\begin{comment}
Anchore offers services in two ways: Anchore Engine and Anchore
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. 
\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get vulnerability feed of various OS distribution, Anchore refers to
different sources. For example Ubuntu launchpad database is used for Ubuntu.
In Ubuntu launchpad database, for a given CVE, there is entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in following form:
\newline \\

\noindent <release>\_<source-package>: <status> (<version/notes>) \\

The status can be anyone of the following:

\textbf{DNE:} It means 'Does Not Exist'. The package (inside the given release) does not exist in the
		archive.

\textbf{needs-triage:} The vulnerability of this package (inside the given release)
		is not known. It needs to be evaluated.  (No version/notes)

\textbf{not-affected:} The package (inside the given release), while related to the
		CVE in some way, is not affected by the issue. Notes should
		provide detailed information, if needed. For e.g
		"not-affected (1.14.6-1.1)" indicates that this specific
		package version in the given release is not affected.

\textbf{needed:} The package (inside the given release) is vulnerable to the
		CVE and needs to be fixed.

\textbf{active:} The package (inside the given release) is vulnerable to the
		CVE, needs fixing, and is actively being worked on.

\textbf{ignored:} The package (inside the given release), while related to the
		CVE in some way, is being ignored for some reason.  The
		notes should provide that reason. For e.g "ignored (reached end-of-life)".
		This means that this given Ubuntu release already reached
		end-of-life so this CVE is ignored by Ubuntu. However, if there
		is an extended security support for this release then this
		CVE will be handled in ESM release.

\textbf{pending:} The package (inside the given release) is vulnerable, and
                  has been fixed but an update has not been yet uploaded or
		  pushlished. The "version" indicates the package version 
		  that contains the fix.

\textbf{deferred:} The package (inside the given release) is vulnerable, but 
                   its fix has been deferred for some reason. The notes
		   should provide further details. If a date is mentioned eg
		   "deferred (2015-02-02)" this date specifies the date when
		   the CVE was deferred.

\textbf{released:} The package (inside the given release) was vulnerable, but
		an update has been already uploaded and published. The package version
		is also mentioned. For e.g "released (1.2.3)"
		specifies the package version in which the fix first appeared.

\textbf{released-esm:} The package (inside the given release) was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.
		The fixed version of such packages is appended by
		+esmN or ~esmN, indicating that this package version is available
		only via ESM.

Figure~\ref{example} illustrates how the information of a CVE is represented
in Ubuntu launchpad database.

\begin{figure}[H]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registery to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.

@@

In this section, we present and compare scanning results of three scanners.

@@

Figure~\ref{fig:graph1} gives more image specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Cnetos contain higher number of critical vulnerabilities than Ubuntu and Alpine.

\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}

\begin{comment}
\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c|c},
	table head ={Image Tag} & {Image Name}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{names.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table2}Image names}
\end{table}
\end{comment}

\begin{figure}[H]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure*}[!htb]
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure*}

@@

Table~\ref{table1} compares results of scanning images with the three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table.

When we add all regions of Venn diagram
we get total 20050 vulnerabilities in Bids and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.
libavlibavlibavlibavlibavlibavlibav
The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

@@

\begin{comment}
Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
both Clair and Vuls.
\end{comment}

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in linux-kernel-headers.
For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities with status
as "not-affected". So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls. In other words, we can say that
these are false positives by Vuls.
For example, we scanned an image having Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
is not affected by this CVE.

\textbf{With CVE status as "Ignored (reached end-of-life)":}
Some vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
only refers ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE", which means does not exist, then Clair Scanner will not report it. 
For example CVE-2017-9994 vulnerability in libav package is ignored in Trusty LTS release due end-of-life.
so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
release so Clair Scanner also do not report it. As Ubuntu 14.04 LTS release is present inside the images still
Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.

@@

\textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find package manager inside the image and then update the image according the package manager it finds.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2} shows number of vulnerabilities that are detected by Anchore after updating these images.

\begin{figure*}[!htb]
        {\includegraphics[width=\textwidth]
        {Figures/afterupdatewithpackage.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}
